Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-06-05 paper/main.tex
Auto Update from local Sharelatex

In the health care domain in the United States the key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA). HIPAA is backed by significant civil penalties as well as specifics about security and what can and cannot be done with protected health information \cite{hippaviol}. There are two primary methods by which data can be shared or made public: de-identification, the removal of specific identifiers or summarization to a level at which individual identification is minimized, and through strict legal relationships called a business associate agreement. Even institutions which share data within the confines of the laws face a steep institutional risk. These legal barriers makes it difficult to enable independent verification of ML models which often require enormous amounts of training data.

Perhaps more ominously and broadly relevant for researchers, on May 25, 2018 the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}. This law establishes a new paradigm in data ``ownership'' for that jurisdiction. This set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing that data to honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.

@@

Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process. All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process. 
\begin{figure}[ht]
  \centering
  \includegraphics[width=120mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}
All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries. Next the processed query is executed against the protected data set and results are passed into the modular synthesis process. While the current implementation only utilizes a couple of synthesis methods, ML developers or data warehouse owners can insert their own custom method or modify existing methods. Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user. Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.

>>>>

Many domains in which ML investigators work have legal barriers that make it difficult to enable independent verification of ML models which frequently require enormous amounts of training data. As an example, in the health care domain in the United States, a key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA). HIPAA is backed by significant civil penalties as well as specifics about security and what can and cannot be done with protected health information \cite{hippaviol}. While there are other domain specific data privacy laws, there are also some broad rules that affect entire countries such as the European Union's General Data Protection Regulation (GDPR). The GDPR puts in place new rules about data ownership and control in an attempt to give individuals more control over their information.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=120mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}

Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process. All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process. All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries. Next the processed query is executed against the protected data set and results are passed into the modular synthesis process. While the current implementation only utilizes a couple of synthesis methods, ML developers or data warehouse owners can insert their own custom method or modify existing methods. Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user. Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
